### 2024-01-27 tesis_Ashish/Chapter7/chapter7.tex
update 27 Jan

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
  \caption[TEPX double disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles. %The planes are separated in z by about 1 cm. The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.
  }
  \label{fig:Innertracker_40}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.1 \columnwidth]{ashish_thesis/edited_tepx_alllayer_v5.png}
  \caption[TEPX double disk]{ \onehalfspacing R-Z view of the TEPX double-disk showing the four layers of modules L1, L2, L3 and L4. Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules. The planes are separated in z by about 1 cm. The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.}
  \label{fig:Innertracker_41}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for  TEPX disks. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value. }
  \label{fig:CMS_4205}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_3.png}
  \caption[TEPX Clusters Fit And Residuals]{\onehalfspacing Left: Simulated mean number of clusters for  TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for TEPX Disk 4 Ring 1. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value. }
  \label{fig:CMS_4206}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_1.png}
  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS_420}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
  \caption[TEPX two-fold coincidences fit And residuals]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS_4207}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=0.5 \columnwidth]{ashish_thesis/tepx_DD.png}
  \caption[X-Y view of TEPX double-disk]{ \onehalfspacing View of one TEPX double-disk in the $r-\phi$ plane; individual pixel modules on two planes (double-disk) and five rings are outlined by yellow rectangles. %The planes are separated in z by about 1 cm. The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.
  }
  \label{fig:Innertracker_40}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.1 \columnwidth]{ashish_thesis/edited_tepx_alllayer_v5.png}
  \caption[R-Z view of TEPX double-disk]{ \onehalfspacing R-Z view of the TEPX double-disk showing the four layers of modules L1, L2, L3 and L4. Layer 1 and 3 has Ring 1, 3 and 5 modules, Layer 2 and 4 has Ring 2 and Ring 4 modules. The planes are separated in z by about 1 cm. The first plane holds modules on both front and back faces, with alternating rings to cover the gaps in r; the second plane holds modules in the same way as the first plane, but with an offset in $\phi$ to cover the gaps in $\phi$.}
  \label{fig:Innertracker_41}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_2.png}
  \caption[TEPX cluster linear fit per disk]{\onehalfspacing Left: Simulated mean number of clusters for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for  TEPX disks. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value. }
  \label{fig:CMS_4205}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_3.png}
  \caption[TEPX clusters linear fit]{\onehalfspacing Left: Simulated mean number of clusters for  TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: %Deviation from linearity for clusters for TEPX Disk 4 Ring 1. The non-linearity is calculated as
    The relative difference between the data points and the values of the fit function at the respective pileup value. }
  \label{fig:CMS_4206}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_1.png}
  \caption[TEPX two-fold coincidences linear fit per disk]{\onehalfspacing Left: Simulated mean number of two-fold coincidences for TEPX disks as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS_420}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{ashish_thesis/michigan_4.png}
  \caption[TEPX two-fold coincidences linear fit for Disk 4 Ring 1]{\onehalfspacing Left: Simulated mean number of two-fold coincidences in phi for TEPX Disk 4 Ring 1 as a function of pileup. A line is fitted between pileup values of 0 and 2, and then extrapolated up to a pileup of 200. Right: The relative difference between the data points and the values of the fit function at the respective pileup value.}
  \label{fig:CMS_4207}
\end{figure}
